%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------    

\cventry
{Research Scientist} % Job title
{Convoy} % Organization
{Seattle WA} % Location
{Sep. 2019 - present} % Date(s)
{
\begin{cvitems}
 \vspace{0.1cm}
\item {Deployed a regression model to predict when a driver will arrive at a facility, improving predicted ETA accuracy by 25\%.\vspace{0.1cm}}
\item {Deployed a model to determine whether we’re tracking the correct driver on a shipment, reducing incorrect driver tracking by 80\%.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Data Scientist} % Job title
{Boeing} % Organization
{Seattle WA} % Location
{Aug. 2018 - Aug. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
 \vspace{0.1cm}
\item {Trained an object detection model (Faster R-CNN) implemented using tensorflow to identify 9 different classes of symbols in engineering drawings. Created synthetic training examples to overcome class imbalances and improve model generalization.\vspace{0.1cm}}
\item {Applied classic image processing techniques and open-source optical character recognition models to interpret text in engineering drawings. \vspace{0.1cm}}
\item {Deployed these models in a continuously running docker container that receives messages from and send results to a kafka server.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Fellow} % Job title
{Insight Data Science} % Organization
{Seattle WA} % Location
{Jan. 2018 - Jul. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
 \vspace{0.1cm}
\item {Built Gefilter Fish, a Chrome extension to cluster Amazon reviews into topics and reduce redundancy by greater than 15\% compared to a current feature on the website.\vspace{0.1cm}}
\item{Designed an interface to display these topics when viewing a product on Amazon's website. It also returns summaries of the reviews focused on that topic.\vspace{0.1cm}}
\item{Performed sentiment analysis using a database of 1.7M reviews to determine the perception of specific aspects of a product.\vspace{0.1cm}}
\item{Used Python, Javascript, SQL, web scraping, and natural language processing techniques such as lemmatization, tf-idf, and non-negative matrix factorization.}
\end{cvitems}
}

%------------------------------------------------  

\cventry
{Graduate/Postdoctoral Researcher} % Job title
{University of Washington} % Organization
{Seattle WA} % Location
{Sep. 2012 - Dec. 2017} % Date(s)
{ 
\begin{cvitems}
 \vspace{0.1cm}
\item{Developed an algorithm to describe how molecules interact with X-ray lasers. This technique was up to 1000 times faster than previous approaches and is now available in the commercial software package Gaussian16 (Fortran77).\vspace{0.1cm}}
%\item{Implemented nonlinear optimization algorithms to converge quantum mechanical wave functions in $\sim$10 times fewer steps (C++).\vspace{0.1cm}}
%\item{Collaborated with a team of 10 experimental researchers to model how muscular proteins bind and release small molecules and how this process can be tracked with X-ray lasers.\vspace{0.1cm}}
\item{13 peer-reviewed publications, 5 oral presentations, 4 conference posters.}
\end{cvitems}
}

%------------------------------------------------   

%\cventry
%{Research Intern} % Job title
%{Gaussian, Inc.} % Organization
%{Wallingford, CT} % Location
%{Summer 2012 \& Winter 2013} % Date(s)
%{ 
%\begin{cvitems}
 %\vspace{0.1cm}
%\%item{Worked with a team of 5 software developers to implement an algorithm to evaluate the energy of a molecular system up to 30\% faster.}
%\end{cvitems}
%}

%------------------------------------------------    

\end{cventries}