%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Publications}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cvpublications}

%------------------------------------------------

\cvpublication
{8.} 
{\textbf{P. J. Lestrange}, Mark R. Hoffmann, X. Li, ``Time-dependent Configuration Interaction using the Graphical Unitary Group Approach: Nonlinear Electric Properties." \textbf{2017}, \textit{Submitted}.} 

%------------------------------------------------

\cvpublication
{7.} 
{D. B. Lingerfelt, \textbf{P. J. Lestrange}, J. J. Radler, S. E. Brown-Xu, P. Kim, F. N. Castellano, L. X. Chen, X. Li, \href{http://pubs.acs.org/doi/abs/10.1021/acs.jpca.6b12099}{``Can Excited State Electronic Coherence be Tuned via Molecular Structural Modification? A First-Principles Quantum Electronic Dynamics Study of Pyrazolate-Bridged Pt(II) Dimers."} \textit{J. Phys. Chem. A}, \textbf{2017}, \textit{121}, 1932-1939.} 

%------------------------------------------------

\cvpublication
{6.} 
{L. X. Chen, M. L. Shelby, \textbf{P. J. Lestrange}, N. E. Jackson, M. W. Mara, K. Haldrup, A. B. Stickrath, D. Zhu, H. Lemke, M. Chollet, B. M. Hoffman, X. Li,  \href{http://pubs.rsc.org/en/Content/ArticleLanding/2016/FD/C6FD00083E}{``Imaging Ultrafast Excited State Pathways in Transition Metal Complexes by X-ray Transient Absorption and Scattering Using X-ray Free Electron Laser Source."} \textit{Faraday Discuss.}, \textbf{2016}, \textit{194}, 639-659.} 

%------------------------------------------------

\cvpublication
{5.} 
{M. L. Shelby, \textbf{P. J. Lestrange}, N. E. Jackson, M. W. Mara, K. Haldrup, A. B. Stickrath, D. Zhu, H. Lemke, B. M. Hoffman, X. Li, L. X. Chen, \href{http://pubs.acs.org/doi/abs/10.1021/jacs.6b02176}{``Ultrafast Processes in the Relaxation of a Nickel(II) Porphyrin Described by Femtosecond X-ray Absorption Spectroscopy."} \textit{J. Am. Chem. Soc.}, \textbf{2016}, \textit{138}, 8752-8764. $^*$\textit{Featured in JACS Spotlights.} \href{http://pubs.acs.org/doi/abs/10.1021/jacs.6b07111}{DOI: 10.1021/jacs.6b07111}} 

%------------------------------------------------

\cvpublication
{4.} 
{\textbf{P. J. Lestrange}, F. Egidi, X. Li, \href{http://scitation.aip.org/content/aip/journal/jcp/143/23/10.1063/1.4937410}{``The Consequences of Improperly Describing Oscillator Strengths Beyond the Electric Dipole Approximation."} \textit{J. Chem. Phys.}, \textbf{2015}, \textit{143}, 234103.} 

%------------------------------------------------

\cvpublication
{3.} 
{B. Peng, \textbf{P. J. Lestrange}, J. J. Goings, M. Caricato, X. Li, \href{http://pubs.acs.org/doi/full/10.1021/acs.jctc.5b00459}{``Energy-Specific Equation-of-Motion Coupled-Cluster Methods for High-Energy Excited States: Application to K-edge X-ray Absorption Spectroscopy."} \textit{J. Chem. Theory Comput.}, \textbf{2015}, \textit{11}, 4146-4153.} 

%------------------------------------------------

\cvpublication
{2.} 
{\textbf{P. J. Lestrange}, P. D. Nguyen, X. Li, \href{http://pubs.acs.org/doi/abs/10.1021/acs.jctc.5b00169}{``Calibration of Energy-Specific TDDFT for Modeling K-edge XAS Spectra of Light Elements."} \textit{J. Chem. Theory Comput.}, \textbf{2015}, \textit{11}, 2994-2999.} 

%------------------------------------------------

\cvpublication
{1.} 
{\textbf{P. J. Lestrange}, B. Peng, F. Ding, G. W. Trucks, M. J. Frisch, X. Li, \href{http://pubs.acs.org/doi/abs/10.1021/ct400765a}{``Density of States Guided M{\o}ller--Plesset Perturbation Theory.''} \textit{J. Chem. Theory Comput.}, \textbf{2014}, \textit{10}, 1910-1914.} 

%------------------------------------------------

\end{cvpublications}
\vspace{-1cm}

